Waveform and Passive Beamforming Design for Intelligent Reflecting Surface-Aided Wireless Information and Power Transfer

### 2020-09-15 main.tex
:pencil: R-E region vs number of subbands

	Figure \ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$. First, it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy. The reason is that although each subband receives a smaller proportion of the total power, it introduces more balanced terms contributing to the output DC current. The result also confirmed that from the perspective of WPT, dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$. As shown in \ref{eq:y_I4} and \ref{eq:y_P4}, the only difference of modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of 2 and $\mathcal{A}\left\{y_{P}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gain. Therefore, superposed waveform enlarges the R-E region for a sufficiently large $N$ (typically no smaller than 4). However, an excessively large $N$ not only requires high computation complexity but also operates out of the small-signal harvester model, thus become prohibitive.
\end{section}

>>>>

	Figure \ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$. \textit{First}, it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy. The reason is that although each subband receives a smaller proportion of the total power, more balanced terms are introduced to further amplify the output DC current, as demonstrated by the scaling laws in \cite{Clerckx2018b}. The result also confirmed that from the perspective of WPT, dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$. As shown in \ref{eq:y_I4} and \ref{eq:y_P4}, the only difference of modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of 2 and $\mathcal{A}\left\{y_{P}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gain. Therefore, superposed waveform enlarges the R-E region for a sufficiently large $N$ (typically no smaller than 4). However, an excessively large $N$ not only requires high computation complexity but also operates out of the small-signal harvester model, thus become prohibitive. \textit{Second}, the R-E region is convex for $N = 2, 4$ and concave-convex for $N = 8, 16$. This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$. When $N$ is in between, the optimal strategy is a combination of both, i.e. a time sharing between the WPT point and the tangent WIPT point obtained by power splitting. Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favouring a different waveform and transmission strategy, both heavily depends on $N$.
\end{section}
